---
title: "Data Processing Pipeline"
author: "Diogo Ribeiro"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Data Processing Pipeline}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = '#>')
library(healthdatascience)
```

This vignette illustrates how to apply the data transformation utilities to a
sample dataset.

## Create Mock Data

```{r mock-data}
set.seed(123)
df <- data.frame(
  mpg = c(mtcars$mpg, NA),
  hp = c(mtcars$hp, 400),
  gear = factor(c(mtcars$gear, 5))
)
```

## Run Transformation Pipeline

```{r pipeline}
steps <- list(
  impute_missing,
  function(d) handle_outliers(d, c('mpg', 'hp'))
)
validators <- list(function(d) all(!is.na(d$mpg)))
clean <- run_transform_pipeline(df, steps, validators)
head(clean)
```

The pipeline imputes missing values, caps extreme outliers and validates that the
`mpg` column contains no missing data after processing.

## Record Data Version

```{r version, eval=FALSE}
record_data_version('processed.csv')
```

Refer to the [Performance Considerations](../docs/performance.md) document for
optimisation tips when scaling these operations.
