---
title: "Latent Class Analysis Workflow"
author: "Diogo Ribeiro"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Latent Class Analysis Workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = '#>')
library(healthdatascience)
```

This vignette demonstrates an end-to-end latent class analysis (LCA) using the
sample NCDB-style data included with the package.

## Load Configuration and Data

```{r load-data}
cfg <- load_config()
init_logging('INFO')
data_path <- system.file('extdata', 'puf_early.csv', package = 'healthdatascience')
```

## Run the LCA Workflow

```{r run-lca, eval=FALSE}
run_lca(
  data_path = data_path,
  output_path = tempfile(fileext = '.RData'),
  config = cfg,
  verbose = TRUE,
  show_progress = TRUE
)
```

The workflow reads the CSV, selects variables, fits the latent class model and
saves the fitted object. Progress messages and a progress bar provide feedback
during execution.

## Inspect Model Output

```{r inspect-model, eval=FALSE}
load('lca_results.RData')
summary(lc7)
```

Refer to the [Statistical Methods](../docs/statistical_methods.md) document for
assumptions underlying LCA.
